---
title: "p8105_hw1_CY2772.Rmd"
author:Chenhui Yan
output: github_document
date: "2024-09-20"
---
#p1
```{r setup, include=FALSE}
# Load the penguins dataset
data("penguins", package = "palmerpenguins")
# Assign number of rows and columns for inline reporting
n_rows <- nrow(penguins)
n_cols <- ncol(penguins)
mean_flipper_length <- mean(penguins$flipper_length_mm, na.rm = TRUE)
```

# Description of the dataset
The `penguins` dataset contains 344 rows and 8 columns. It includes data on various characteristics of penguins, such as their species, island, bill length, bill depth, flipper length, body mass, and sex. 
One important variable, `species`, includes three values: "Adelie", "Chinstrap", and "Gentoo". Another variable of interest is `flipper_length_mm`, which measures the penguin's flipper length in millimeters. The mean flipper length across all penguins in the dataset is 200.92 mm.

```{r}
library(ggplot2)

# Scatterplot of flipper length vs bill length
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(
    title = "Scatterplot of Flipper Length vs Bill Length",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)",
    color = "Species"
  ) +
  theme_minimal()

# Save plot to file
ggsave("scatterplot_flipper_vs_bill.png", width = 6, height = 4)

```

