---
title: "p8105_hw1_CY2772.Rmd"

output: github_document
date: "2024-09-20"
---
Problem1
```{r}
# Load the penguins dataset
data("penguins", package = "palmerpenguins")
# Assign number of rows and columns for inline reporting
n_rows = nrow(penguins)
n_cols = ncol(penguins)
mean_flipper_length = mean(penguins$flipper_length_mm, na.rm = TRUE)
```
Description of the Dataset:

The penguins dataset contains 344 rows and 8 columns. It includes data on various characteristics of penguins, such as their species, island, bill length, bill depth, flipper length, body mass, and sex. 

One important variable, species, includes three values: "Adelie", "Chinstrap", and "Gentoo". Another variable of interest is flipper_length_mm, which measures the penguin's flipper length in millimeters. The mean flipper length across all penguins in the dataset is 200.92 mm.


```{r}
library(ggplot2)

# Scatterplot of flipper length vs bill length
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(
    title = "Scatterplot of Flipper Length vs Bill Length",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)",
    color = "Species"
  ) +
  theme_minimal()

# Save plot to file
ggsave("scatterplot_flipper_vs_bill.png", width = 6, height = 4)

```

Problem2
```{r}
library(tidyverse)
#Create a random sample of size 10 from a standard Normal distribution
random_sample = rnorm(10)
#Create a  logical vector indicating whether elements of the sample are greater than 0
logical_vector = random_sample > 0
#Create a character vector of length 10
character_vector = c("A","B","C","D","E","F","G","H","I","J")
#Create a factor vector of length 10, with 3 different factor “levels”
factor_vector = factor(rep(c("low","medium","high"), length.out = 10))
# Combine into a data frame
hw1_df = data.frame(
  random_sample = random_sample,
  logical_vector = logical_vector,
  character_vector = character_vector,
  factor_vector = factor_vector
)
#Attempt to calculate the means for each variables
mean_random_sample = mean(hw1_df$random_sample)
mean_logical_vector = mean(hw1_df$logical_vector)
# mean_character_vector = mean(hw1_df$character_vector) #cause error
# mean_factor_vector = mean(hw1_df$factor_vector) #cause error

# Coerce character and factor variables to numeric
numeric_character_vector = as.numeric(hw1_df$character_vector)
numeric_factor_vector = as.numeric(hw1_df$factor_vector)

# Calculate the mean of each variable after coercion
mean_character_vector = mean(numeric_character_vector)
mean_factor_vector = mean(numeric_factor_vector)

#Print the means
cat("The mean of the random_sample is:",  mean_random_sample )
cat("The mean of the logical_vector is" , mean_logical_vector )
cat("The mean of the character_vector is", mean_character_vector)
cat("The mean of the factor_vector is", mean_factor_vector)
```

