---
title: "p8105_hw1_CY2772.Rmd"

output: github_document
date: "2024-09-20"
---
# Problem 1
The problem focus on writing a short description of the penguins dataset which include:

* The data in this dataset, including names / values of important variables

* The size of the dataset

* The mean flipper length

* Make a scatterplot

```{r}
# Load the penguins dataset
data("penguins", package = "palmerpenguins")
# Assign number of rows and columns for inline reporting
n_rows = nrow(penguins)
n_cols = ncol(penguins)
mean_flipper_length = mean(penguins$flipper_length_mm, na.rm = TRUE)
```
## Names of the dataset
The names of the data in penguins dataset is showed using the following code:
```{r plot_names, collapse=TRUE}
ls(penguins)
```
It shows that the names in the penguins dataset are: `r ls(penguins)`

## Description of the Dataset:
* The penguins dataset contains 344 rows and 8 columns. It includes data on various characteristics of penguins, such as their species, island, bill length, bill depth, flipper length, body mass, and sex. 

* One important variable, species, includes three values: "Adelie", "Chinstrap", and "Gentoo". Another variable of interest is flipper_length_mm, which measures the penguin's flipper length in millimeters. The mean flipper length across all penguins in the dataset is 200.92 mm.

## Making the scatterplot
```{r}
#make the scatterplot
library(ggplot2)

# Scatterplot of flipper length vs bill length
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(na.rm = TRUE) +
  labs(
    title = "Scatterplot of Flipper Length vs Bill Length",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)",
    color = "Species"
  ) +
  theme_minimal()

# Save plot to file
ggsave("scatterplot_flipper_vs_bill.png", width = 6, height = 4)

```

# Problem 2
This problem focus on create a data frame comprised of:

  * A random sample of size 10 from a standard Normal distribution

  * A logical vector indicating whether elements of the sample are 
  greater than 0

  * A character vector of length 10

  * A factor vector of length 10, with 3 different factor “levels”

And try to take the mean of each variable in the dataframe.

## Create data frame
### Create 4 variables
```{r}
library(tidyverse)
#Create a random sample of size 10 from a standard Normal distribution
random_sample = rnorm(10)
#Create a  logical vector indicating whether elements of the sample are greater than 0
logical_vector = random_sample > 0
#Create a character vector of length 10
character_vector = c("A","B","C","D","E","F","G","H","I","J")
#Create a factor vector of length 10, with 3 different factor “levels”
factor_vector = factor(rep(c("low","medium","high"), length.out = 10))
```
### Combine vectorinto a data frame
```{r}
hw1_df = data.frame(
  random_sample = random_sample,
  logical_vector = logical_vector,
  character_vector = character_vector,
  factor_vector = factor_vector
)
```
## Attempt to calculate the means for each variables
Next, try to take the mean of each variable of the dataframe(hw1_df) using pull function in the tidyverse package:
```{r mean_pull}
mean(pull(hw1_df, random_sample))
mean(pull(hw1_df, logical_vector))
mean(pull(hw1_df, character_vector))
mean(pull(hw1_df, factor_vector))
```
The result indicates that it's possible to calculate the mean of numeric and logical variables, but it's not applicable for character or factor variables. To handle this, we can use the as.numeric function to attempt converting character and factor variables into numeric ones.

### Coerce character and factor variables to numeric
```{r}
numeric_character_vector = as.numeric(hw1_df$character_vector)
numeric_factor_vector = as.numeric(hw1_df$factor_vector)
```

### Calculate the mean of each variable after coercion
```{r}
mean_character_vector = mean(numeric_character_vector)
mean_factor_vector = mean(numeric_factor_vector)
```
### Print the means
```{r}
cat("The mean of the random_sample is:",  mean(pull(hw1_df, random_sample)) )
cat("The mean of the logical_vector is" , mean(pull(hw1_df, logical_vector)) )
cat("The mean of the character_vector is", mean_character_vector)
cat("The mean of the factor_vector is", mean_factor_vector)
```

